%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer Intern} % Job title
    {Housing \& Development Board (HDB)} % Organization
    {Singapore} % Location
    {May. 2018 - Aug. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Redesigned the key workflow (performed 60 - 80 times per day per inspector) of the existing mobile application used by inspectors to perform site inspection, thereby reducing the number of steps required to perform this workflow from 8 to 3.}
        \item {Redesigned 2 other workflows, thereby reducing the number of keystrokes required to perform them from 8 to 2 and 7 to 2.}
        \item {Enhanced existing features and suggested new features, thereby improving the productivity and quality of the inspectors' work.}
        \item {Redesigned the User Interface to be compatible with the improvements made above.}
        \item {Automated the monthly generation of inspection schedule, reducing the amount of time taken to generate the schedule from 1 day to 15 minutes.}
        \item {Gathered User Requirements from scratch and continually verified my prototype with users. This helped me to develop relevant solutions (as seen above) which will eventually be fully developed by HDB's IT Department and deployed for the inspectors to use.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer Intern} % Job title
    {National University of Singapore - Open Source Software (NUS - OSS) (10k LoC, 1k commits)} % Organization
    {Singapore} % Location
    {May. 2017 - Aug. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on \href{https://github.com/issues?utf8=\%E2\%9C\%93&q=repo\%3Ase-edu\%2Faddressbook-level4+involves\%3AZhiyuan-Amos}{Addressbook-Level4}, a Java application used to teach NUS Computer Science (CS) students about Software Engineering. This is a compulsory module for all NUS CS students. As a result, this project demands high standards of code quality, and working on this project taught me how to write quality code, and I became familiar with Software Engineering patterns.}
        \item {Mentored a student under the Google Summer of Code program and guided new contributors by discussing with them on how to improve on the existing code architecture and reviewing their code.}
        \item {Wrote missing unit, integration and system tests, increasing test coverage from 90\% to 92\%.}
        \item {Designed and wrote code to implement new features such as allowing the user to undo and redo their actions.}
        \item {Continued contributing after the internship stint till today. Estimated contribution: \href{https://github.com/se-edu/addressbook-level4/graphs/contributors}{14.4k LoC changed}, \href{https://github.com/se-edu/addressbook-level4/pulls?utf8=\%E2\%9C\%93&q=is\%3Apr+is\%3Aclosed+author\%3AZhiyuan-Amos+is\%3Amerged}{90 PRs merged}}
      \end{cvitems}
    }
 
%---------------------------------------------------------

  \cventry
    {Tutor - Programming Methodology} % Affiliation/role
    {NUS} % Organization/group
    {Singapore} % Location
    {Aug. 2016 - Nov. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Taught a class of 12 undergraduate students on fundamental concepts of problem solving using C language, on a weekly basis. Also assessed their understanding \& provided feedback for improvement.}
        \item {Achieved Overall Teaching Effectiveness Score of 4.40 / 5}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
