%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Cocurricular Activity}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {Committer} % Affiliation/role
    {\href{https://github.com/exercism}{Exercism}} % Organization/group
    {} % Location
    {Jan. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Exercism aims to help users improve their programming skills in many different languages through writing code and submitting it to Exercism for feedback.}
        \item {Suggested improvements for existing suite of test cases and updated these test cases. Users attempting these exercises will now have a cleaner suite of test cases to refer to. See pull requests \href{https://github.com/exercism/problem-specifications/pull/1118}{\color{teal}\#1118}, \href{https://github.com/exercism/problem-specifications/pull/1119}{\color{teal}\#1119} and the corresponding issues.}
        \item {Implemented the model answer and the tests for an algorithmic exercise. Users are now able to attempt this new exercise. See pull request \href{https://github.com/exercism/java/pull/1188}{\color{teal}\#1188}.}
      \end{cvitems}
    }

  \cventry
    {Participant} % Affiliation/role
    {Microsoft Azurenaut Hackathon} % Organization/group
    {Singapore} % Location
    {Jan. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Created a chatbot in a team of 3 that provides information about NUS, such as the estimated arrival times for the next bus and the availability of car park lots. This project aims to integrate existing mobile applications such as NUS Carparks and NUS NextBus into a single application.}
      \end{cvitems}
    }
    
  \cventry
    {Temasek Junior College (TJC)} % Degree
    {Edusave Awards for Achievement, Good Leadership and Service (EAGLES)} % Institution
    {Singapore} % Location
    {2012} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {National Inter-school Wushu Championships 3rd and 4th position}
        \item {Performer in National Day Parade}
        \item {Class Chairperson: 2011 - 2012}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
