%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Associate Engineer Intern} % Job title
    {SingPilot Pte Ltd)} % Organization
    {Singapore} % Location
    {Jan. 2018 - Aug. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Achieved A for the 8 month work attachment known as SIT’ Integrated Work Study Programme}
        \item {Performed R/&D of autonomous driving technology}
        \item {Carried out hardware & software debugging and handled the procurement process in the project.}
        \item {Oversaw the process of design, develop, manufacture and testing of the electromechanical subsystem which led to the integration of design systems with the electric vehicle}
        \item {Led the team with integration of the various electromechanical sub-systems into electric vehicle.}
        \item {Carried out hardware & software debugging and handled the procurement process in the project.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Etest Semiconductor Programmer Intern} % Job title
    {Globalfoundries Pte Ltd} % Organization
    {Singapore} % Location
    {Apr. 2013 - Oct. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created an Etest Offline Simulator to support the Etest simulation for cost savings, catching error and bugs before actual process work.}
        \item {Analysed and improved requirements with stakeholders for the Etest offline simulator. }
        \item {Worked with the ETest process and used the cleanroom with the Standard Operating Procedure.}
        \item {Designed and improve test case for the new features by 72% to 80% in the Etest Offline Simulator }
      \end{cvitems}
    }
\end{cventries}
